Integrating brain and biomechanical models - a new paradigm for understanding neuro-muscular control

### 2017-12-05 papers/integration/omm_integ.tex
Completes revision of discussion

\def\Address{\\
$^{1}$Adaptive Behaviour Research Group, Department of Psychology,
  The University of Sheffield, Sheffield, UK \\
$^{2}$Insigneo Institute for in-silico Medicine,
  The University of Sheffield, Sheffield, UK \\
$^{3}$Department of Computer Science,
  The University of Sheffield, Sheffield, UK \\
$^{4}$Department of Automatic Control Systems Engineering,
  The University of Sheffield, Sheffield, UK \\
$^{5}$Department of Electrical and Computer Engineering,
  The University of Patras, Patras, Greece \\
}

@@

There is a long history of modelling the oculomotor system. For a
comprehensive review, see \cite{girard_brainstem_2005}. Models of
individual \rvw{sub-systems} have been proposed for brainstem
\citep{robinson_oculomotor_1975,scudder_new_1988,gancarz_neural_1998},
cerebellum \citep{quaia_model_1999,dean_modelling_1995,dean_learning_1994}
and superior colliculus
\citep{arai_two-dimensional_1994,moren_mechanism_2013,marino_spatial_2012}.
More recently, combined models have also been developed incorporating
sensory input \citep{cope_basal_2017} and driving \rvw{a second order
differential equation} representing the eye
\citep{tabareau_geometry_2007,nguyen_saccade_2014,thurat_biomimetic_2015}.
None of these models has yet fully closed the loop to produce a
behaving system operating freely within its environment. We argue that
developing integrated, closed-loop models of behaving systems offers
insights into the operation of neural systems that are not available
from input-~or output-assumption models.

@@

The saccadic burst generator model was originally conceived with the
assumption of a step input, which returns to zero activity at a
suitable time to curtail the saccade and avoid staircase
saccades \citep{gancarz_neural_1998}. In our model there is no such
mechanism to reduce activity in SC\_deep, and elsewhere.  Although a
successful, accurate saccade towards a target luminance will remove
the excitation which caused the activity in SC\_deep by bringing the
target luminance within the masked, foveal region, the activity in SC
decays too slowly to avoid additional saccadic movements. We found it
necessary to hypothesise an inhibitory feedback mechanism from the SBG
to the brain model.  This is shown in Fig.~\ref{fig:sbg}, which indicates
how the output from the inhibitory burst neurons (IBN) of the SBG
model are used to feed back an inhibitory signal to the SC\_deep,
thalamus and FEF populations in the brain model, resetting them ready
for the next saccade.
% Might have to justify the above a bit more.

@@

To verify that our implementation of the brain model has the same
functionality as that reported in \cite{cope_basal_2017}, we
investigated the effect on saccadic response times of: target
eccentricity; and any gap or overlap between fixation off-time and
target on-time. We showed that the full model reproduces the `hockey
stick' shape shown in Fig. 7 of \cite{cope_basal_2017} for horizontal
[Fig.~\ref{lat_vs_all}(a)], vertical [Fig.~\ref{lat_vs_all}(b)] and
oblique saccades (not shown). The latency increases with eccentricity
far from the fovea because the retinotopic mapping reduces the
activity in the basal ganglia for more eccentric targets (see
Fig.~\ref{mapping}). Closer to the fovea, the \rvwt{effect of} the
foveal mask \rvwt{on} the activity in FEF again leads to reduced input
into the basal ganglia and an increased time to achieve disinhibition
in SNr.

@@

\rvw{Modern programming platforms, often originating from the world
of computer gaming, make it relatively easy to model a virtual
environment. Consequently, an increasing number of studies into
robotic or neuro-mimetic control are carried out with virtual robots
operating within a virtual environment. \cite{arena_motor-skill_2017}
describes a robotic insect system based on the fly
species \e{Drosophila Melanogaster}. It has biomimetic insect legs
implemented in a virtual robot and a neuro-mimetic brain. Closing the
loop is a visual sensory input system which is able to determine the
distance between the robot and an obstacle and the obstacle's
height. The visual system is not described in detail and may not be
biologically modelled (much in the way that the visual processing
stream is not modelled in detail in the present work). Nevertheless,
this study may reasonably be described as compuational neurobehaviour;
the authors demonstrate that the virtual robot is able to learn to
climb obstacles in a realistic manner and suggest that the model may
be compared with experimental data from future Drosophila experiments
addressing obstacle climbing and learning.}
%
\rvw{\cite{nguyen_saccade_2014} and
\cite{thurat_biomimetic_2015} are two studies of the oculomotor system
which model sensory input, neural control and motor output. These
studies fall outside the remit of computational neurobehaviour only
because they omit to close the sensory
loop. \cite{dewolf_spiking_2016} describes a reach model comprising a
simplified virtual arm (with fewere degrees of freedom than a primate
arm), and a biologically inspired brain model. This model also omits
to close the sensory feedback loop and we consider it a traditional
computational neuroscience study.}

@@

The implementation of a biophysically accurate model of the eye, and
the closed-loop nature of the model makes it very natural to consider
how the model will behave making saccades from arbitrary starting
positions, or how it would respond to a sequence of stimuli. This was
the motivation for the out-and-return experiment (Fig.~\ref{outrtn})
as well as for the double step experiment (Fig.~\ref{doublesteps}).
We found that return saccades were substantially affected by the
biomechanics of the eye, as the brain and brainstem model had no
mechanism to account for the position-dependent restoring forces
applied by the eye. This question has been addressed by other authors;
\cite{groh_effects_2011} investigates the effect of
initial eye position on stimulated saccades and finds a need for the
signal in superior colliculus to be modulated by an eye position
signal. \cite{ling_effects_2007} shows the existence of a position
dependent firing rate offset in abducens neurons. Though we will not
speculate here on the mechanism by which return saccades may be made
accurate whilst also resetting the activity of tonic neurons in the
SBG, it is interesting that in the model in which we omitted to reset
TN activity (TModel4), we obtained relatively accurate out-and-return
saccades which closely resembled experimental data.  We suggest that
residual activity in TN populations may offer an explanation for how
the restorative force exerted by the elastic oculomotor muscles is
compensated for. A comparison of this idea with that
of \cite{groh_effects_2011} (that there is a modulation, from a
brainstem signal, of the SC readout) would make a subject for a future
study. Although these existing studies have highlighted this issue,
the inaccurate return saccades which the model makes from eccentric
starting positions provide a clear example of the way in which
integrating known models into a closed-loop system can highlight
deficiencies in the model.

@@

An examination of the behaviour of the model when presented with
`double-step stimuli' reveals a problem with this scheme. We found
that when double-step stimuli were presented (where an initial target
at 8\dg~was replaced with a 12\dg~target after 30 or 40~ms) and a
double saccade was made [Fig.~\ref{doublesteps}(a), black lines] the
second saccade latency was \e{longer} even than the initial
saccade. This contrasts with \cite{becker_analysis_1979} who find that
second, corrective saccades occur with \e{shorter} latencies.  This
suggests that the inhibitory reset signal implemented in this model is
too strong or has the wrong timescales. This issue highlights the fact
that connections \e{between} component models are quite as important
as the connections within each model.

@@

% Reviewer 1's point 2.
\rvw{\bol{FIXME}. We should consider whether inaccuracies within one sub-system,
such as the musculo-skeletal model, may introduce errors that
propagate through the closed loop system and cannot be counteracted by
the nervous system part of the simulation.  My thoughts: You have to
do this alongside other research so that sub-systems are informed by
the best knowledge available.
%
How can you (or someone using this or related models)
exclude introducing (biomechanical) properties that are not present in
the biological system, or make sure to not miss critical biomechanical
properties that might help remedy some of the shortcomings of the
closed loop model?.}

@@

\begin{figure}[htb!]
\begin{center}
\includegraphics[width=\textwidth]{./figures/ccg_model.png}
\end{center}
\textbf{\refstepcounter{figure}\label{fig:ccg_model} Figure \arabic{figure}.}
{ \bol{a) The macroscopic architecture of the \ccg~model.} The main
nuclei modelled as brain systems are: basal ganglia (BG), frontal eye
fields (FEF), thalamus (THAL) and superior colliculus (SC). The
retinal input is presented via non-biologically plausible retinal
populations. The loops through basal ganglia, which define the
architecture, are shown with coloured lines: the cortical loop
(through FEF and THAL) in green and the sub-cortical loop (through SC
and THAL) in blue. Connections with arrowheads indicate excitatory
connections, those with circles are inhibitory. A red border indicates
that the box represents a sub-system of two or more populations; a
black box indicates (at least, within the context of the model) a
single neural population. The BG box is expanded in: \bol{b) The basal
ganglia model component.}
%
This shows a basal ganglia comprising striatum (Str\_D1 \& Str\_D2),
subthalamic nucleus (STN), globus pallidum externum (GPe) and
substantia nigra reticulata (SNr). The model has three action channels
shown as black boxes within each blue population border. Three
channels of cortical input to the BG are also depicted. Red indicates
the activation level of a given channel, helping to illustrate the
selection mechanism. For example, the channel indicated by the
leftmost bar has a high salience (cortical input) and excites activity
in Str\_D1 which then inhibits the leftmost bar in SNr. The diffuse
projection from STN is equivalent to summing its projections
channel-wise, and then projecting the sum to all channels of its
target populations (the blue arrows indicate that all channels of GPe
and SNr are targeted by the connection). Dopaminergic modulation of
the inputs to the striatum are indicated by the blue circles labelled
`d' and the dotted lines. The SNr sends inhibitory output projections
to its targets. \bol{c) 2D Gaussian weights.} The `GaussianKernel'
connectivity pattern is based on the `in-plane displacement' between
the location of a neural element in one layer, and the location of a
target neural element in the target layer for the connection. The
potential weight of the connection is given by a 2D Gaussian function,
which is maximum for the target neuron which exactly corresponds to
the source neuron, and drops down for target neurons which are
horizontally displaced from the source neuron. A threshold is applied
to avoid a computationally expensive all-to-all connectivity (with
most of these connections having negligible weight values).  If the
weight is non-zero, then a connection is made from source to target,
otherwise no connection is made. \bol{d) Gaussian connectivity.} This
image shows connectivity (green rays) from two source neurons (in
Str\_D2, brown spheres) to target neurons (in GPe, blue spheres). The
circular connectivity pattern is seen. This does not show the weight
\e{values}, which reduce `towards the edge of the circle' and follow the
relationship shown in (c).}
\end{figure}

\begin{figure}[htb!]
\begin{center}
\includegraphics[width=0.9\textwidth]{./figures/Brain_Model.png}
\end{center}
\textbf{\refstepcounter{figure}\label{brain_model} Figure \arabic{figure}.}
{ The brain model. This is the SpineCreator `network layer' view of
the model. Each box represents a neural population with 2500 elements,
arranged in a 50$\times$50 grid. The SpineML component name is printed
on the bottom right corner of each population box and the population
name is at the top. The overall connectivity between populations is
represented by the projection arrows with the colour indicating the
connectivity scheme (one-to-one connections are red, Gaussian kernel
connections are dark blue and so on). Excitatory connections have
arrowheads and inhibitory connections have circles, although for
details of the behaviour of the connections, the weight-update and
post-synapse components must be studied. Briefly, the model comprises
a \e{World} population, into which a retinotopically organised view of
the world is introduced. This information is passed into cortical
populations (FEF) and subcortical populations (SC) via a simple model
of the retina. These feed a cortico-thalamo-basal ganglia loop, which
selects which region of the deep layer of superior colliculus should
be disinhibited, allowing activity to build up therein. The five
populations comprising the basal ganglia are enclosed in a grey
outline. Note that substantia nigra pars compacta is not modelled
here, instead the level of dopamine in the striatum is set via a
parameter in the Str\_D1 and Str\_D2 populations}
\end{figure}

\begin{figure}[htb!]
\begin{center}
\includegraphics[width=0.9\textwidth]{./figures/mapping.png}
\end{center}
\textbf{\refstepcounter{figure}\label{fig:mapping} Figure \arabic{figure}.}
{ Representative mapping from eye's frame of reference in Cartesian
co-ordinates to retinotopic co-ordinates. (a) The mapping of
luminances in the eye's frame of reference. The world input is
pre-defined by a JSON configuration file. Luminance position, size and
shape can be defined in this file, along with the times at which
luminances appear and disappear. The worldDataMaker.cpp code computes
the locations of the luminances in the eye's frame of reference, given
its rotational state. It also computes a 2D Gaussian convolution of
the luminances. Here, there are two cross shaped luminances spanning
10\dg, one of value 0.8 at the fixation point (0,0) and one of value
0.5 at a peripheral position (0,-12\dg). Note that these crosses have
the same `bar width' of 2\dg~as the crosses used in the simulations,
but their span of 10\dg~is greater than the 6\dg~used in the
simulations, to make these images clearer. (b) The locations of the
luminances in the eye's frame of reference are then converted into
retinotopic co-ordinates, with centrally located luminances being
represented at low values of $r$ and more peripheral luminances having
higher values of $r$. $\phi$ encodes rotational angle: 1 and 50 encode
upward movement; 13 is left; 25 is down; 37 is right. The output of
the World component is fed into FEF\_add\_noise and into the retinal
neuron populations. The colour map makes it possible to distinguish
between the two crosses. (c) The FEF\_add\_noise populations adds a
level of noise to the signal representing processing of the signal in
visual cortex. (d) A Gaussian projection from FEF\_add\_noise to FEF
further blurs the activity in FEF. FEF is the input to the basal
ganglia and one input to superior colliculus.}
\end{figure}

\begin{figure}[htb!]
\begin{center}
\includegraphics[width=0.6\textwidth]{./figures/Brain_Stem_1channel.png}
\end{center}
\textbf{\refstepcounter{figure}\label{fig:sbg} Figure \arabic{figure}.}
{ One pair of channels of the saccadic burst generator (SBG) for left
(cyan) or right (green) movements. Collicular activity in SC\_avg
excites the channels via SBG weight maps. Each box represents a neural
population and shows the population name, the number of neural
elements (here 2500 or 1) and the SpineML component name; \e{LIN} for
Leaky integrator or \e{integrator}. Key: LLBN: Long lead burst
neurons; IBN: Inhibitory burst neurons; OPN: Omnipause neurons; EBN:
Excitatory burst neurons; TN: Tonic neurons; MN: Motoneurons.}
\end{figure}

\begin{figure}[htb!]
\begin{center}
\includegraphics[width=0.5\textwidth]{./figures/eye_screen_plus.png}
\end{center}
\textbf{\refstepcounter{figure}\label{fig:bioeye} Figure \arabic{figure}.}
{ The biomechanical eye. a) an OpenSim rendering of a pair of
biomechanical eyes showing the positions of the extraocular
muscles. Note that i) volume visualization of muscles should not be
confused with FEM muscle models; it is provided for user feedback
purposes, i.e. shape and color change depending on the muscle
activation, ii) superior and inferior oblique are visualized up to
their respective muscle pulleys. b) OpenSim rendering of biomechanical
eye within a head model c) Top-down schematic cross-sectional view of
the biomechanical eye situated within a spherical screen, with a
horizontal rotation towards a luminances at an angle of $-\theta_{y}$
about the $y$ axis. The $y$ axis points up, out of the page.}
\end{figure}

\begin{figure}[htb!]
\begin{center}
\includegraphics[width=0.9\textwidth]{./figures/model_framework.png}
\end{center}
\textbf{\refstepcounter{figure}\label{model_framework} Figure \arabic{figure}.}
{ The model framework. The model is specified using a combination of
declarative XML files and hand-coded C++. These original model
specifications are shown within the blue box. b) The green box shows
the processes which are applied to the model specification to produce
the BRAHMS system. Most of the process is defined within the scripts
which make up \stob, but the hand-written components must be manually
compiled and installed within the BRAHMS Namespace, allowing the
BRAHMS executable to locate them at runtime. c) The red box shows the
resulting BRAHMS system ready to be executed by the BRAHMS
executable. In practice, this call is made by \stob.}
\end{figure}

\begin{figure}[htb!]
\begin{center}
\includegraphics[width=0.9\textwidth]{./figures/scdeep_plus.png}
\end{center}
\textbf{\refstepcounter{figure}\label{scdeep} Figure \arabic{figure}.}
{ a) \& b) Tabareau-style weight maps for `left' and `down' components
of a saccade. c) The two weight maps in a) and b) shown on the same
graph, viewed from above. Circles show the locations of potential
hills of activity. Purple, dashed circles encode saccades down;
red circles encode saccades with both a left and a down component. d)
Showing the additional deep layer of superior colliculus (SC\_deep2)
and the output layer (SC\_avg, named for the fact that in an earlier
version of the model, it received the output of the centroid of
SC\_deep).  The widening Gaussian projection is shown as the arrow
between SC\_deep and SC\_deep2.}
\end{figure}

\begin{figure}[htb!]
\begin{center}
\includegraphics[width=0.8\textwidth]{./figures/sacc_vs_targetpos.png}
\end{center}
\textbf{\refstepcounter{figure}\label{sacc_vs_targ} Figure \arabic{figure}.}
{ Accuracy at different target eccentricities for fixation luminance
0.2 and target luminance 0.3.}
\end{figure}

>>>>

\def\Address{
$^{1}$Adaptive Behaviour Research Group, Department of Psychology,
  The University of Sheffield, Sheffield, UK \\
$^{2}$Insigneo Institute for in-silico Medicine,
  The University of Sheffield, Sheffield, UK \\
$^{3}$Department of Computer Science,
  The University of Sheffield, Sheffield, UK \\
$^{4}$Department of Automatic Control Systems Engineering,
  The University of Sheffield, Sheffield, UK \\
$^{5}$Department of Electrical and Computer Engineering,
  The University of Patras, Patras, Greece
}

@@

There is a long history of modelling the oculomotor system. For a
comprehensive review, see \cite{girard_brainstem_2005}. Models of
individual \rvw{sub-systems} have been proposed for brainstem
\citep{robinson_oculomotor_1975,scudder_new_1988,gancarz_neural_1998},
cerebellum \citep{quaia_model_1999,dean_modelling_1995,dean_learning_1994}
and superior colliculus
\citep{massone_neural-network_1994,arai_two-dimensional_1994,moren_mechanism_2013,marino_spatial_2012}.
More recently, combined models have also been developed incorporating
sensory input \citep{cope_basal_2017} and driving \rvw{a second order
differential equation} representing the eye
\citep{tabareau_geometry_2007,nguyen_saccade_2014,thurat_biomimetic_2015}.
None of these models has yet fully closed the loop to produce a
behaving system operating freely within its environment. We argue that
developing integrated, closed-loop models of behaving systems offers
insights into the operation of neural systems that are not available
from input-~or output-assumption models.

@@

The saccadic burst generator model was originally conceived with the
assumption of a step input, which returns to zero activity at a
suitable time to curtail the saccade and avoid staircase
saccades \citep{gancarz_neural_1998}. In our model there is no such
mechanism to reduce activity in SC\_deep, and elsewhere.  Although a
successful, accurate saccade towards a target luminance will remove
the excitation which caused the activity in SC\_deep by bringing the
target luminance within the masked, foveal region, the activity in SC
decays too slowly to avoid additional saccadic movements. We found it
necessary to hypothesise an inhibitory feedback mechanism from the SBG
to the brain model.  This is shown in Fig.~\ref{fig:sbg}, which
indicates how the output from the inhibitory burst neurons (IBN) of
the SBG model are used to feed back an inhibitory signal to the
SC\_deep, thalamus and FEF populations in the brain model, resetting
them ready for the next saccade. \rvw{There is evidence for inhibitory
projections to SC from the propositus
hypoglossi nucleus \citep{corvisier_possible_1991}, which lies within the
brainstem, upstream from motoneurons, and has been shown to encode eye
velocity \citep{dale_nucleus_2013}.}

@@

To verify that our implementation of the brain model has the same
functionality as that reported in \cite{cope_basal_2017}, we
investigated the effect on saccadic response times of: target
eccentricity; and any gap or overlap between fixation off-time and
target on-time. We showed that the full model reproduces the `hockey
stick' shape shown in Fig. 7 of \cite{cope_basal_2017} for horizontal
[Fig.~\ref{lat_vs_all}(a)], vertical [Fig.~\ref{lat_vs_all}(b)] and
oblique saccades (not shown). The latency increases with eccentricity
far from the fovea because the retinotopic mapping reduces the
activity in the basal ganglia for more eccentric targets (see
Fig.~\ref{fig:mapping}). Closer to the fovea, the \rvwt{effect of} the
foveal mask \rvwt{on} the activity in FEF again leads to reduced input
into the basal ganglia and an increased time to achieve disinhibition
in SNr.

@@

\rvw{Modern programming platforms, often originating from the
computer game industry, make it relatively easy to model a virtual
environment. Consequently, an increasing number of studies into
robotic or neuro-mimetic control are carried out with virtual robots
operating within a virtual environment. \cite{arena_motor-skill_2017}
describes a robotic insect system based on the fly
species \e{Drosophila Melanogaster}. It has biomimetic insect legs
implemented in a virtual robot and a neuro-mimetic brain. Closing the
loop is a visual sensory input system which is able to determine the
distance between the robot and an obstacle and the obstacle's
height. The visual system is not described in detail and may not be
biologically modelled (much in the way that the visual processing
stream is not modelled in detail in the present work). Nevertheless,
this study may reasonably be described as compuational neurobehaviour;
the authors demonstrate that the virtual robot is able to learn to
climb obstacles in a realistic manner and suggest that the model may
be compared with experimental data from future Drosophila experiments
addressing obstacle climbing and learning.}
%
\rvw{\cite{nguyen_saccade_2014} and
\cite{thurat_biomimetic_2015} are two studies of the oculomotor system
which model sensory input, neural control and motor output. These
studies fall outside the remit of computational neurobehaviour only
because they omit to close the sensory
loop. \cite{dewolf_spiking_2016} describes a reach model comprising a
simplified virtual arm (with fewere degrees of freedom than a primate
arm), and a biologically inspired brain model. This model also omits
to close the sensory feedback loop and we consider it a traditional
computational neuroscience study.}

@@

The implementation of a biophysically accurate model of the eye, and
the closed-loop nature of the model makes it very natural to consider
how the model will behave when making saccades from arbitrary starting
positions, or how it would respond to a sequence of stimuli. This was
the motivation for the out-and-return experiment (Fig.~\ref{outrtn})
as well as for the double step experiment (Fig.~\ref{doublesteps}).
We found that return saccades were substantially affected by the
biomechanics of the eye, as the brain and brainstem model had no
mechanism to account for the position-dependent restoring forces
applied by the eye. This question has been addressed by other authors;
\cite{groh_effects_2011} investigates the effect of
initial eye position on stimulated saccades and finds a need for the
signal in superior colliculus to be modulated by an eye position
signal. \cite{ling_effects_2007} shows the existence of a position
dependent firing rate offset in abducens neurons. Though we will not
speculate here on the mechanism by which return saccades may be made
accurate whilst also resetting the activity of tonic neurons in the
SBG, it is interesting that in the model in which we omitted to reset
TN activity (TModel4), we obtained relatively accurate out-and-return
saccades which closely resembled experimental data.  We suggest that
residual activity in TN populations may offer an explanation for how
the restorative force exerted by the elastic oculomotor muscles is
compensated for. A comparison of this idea with that
of \cite{groh_effects_2011} (that there is a modulation, from a
brainstem signal, of the SC readout) would make a subject for a future
study. Although these existing studies have highlighted this issue,
the inaccurate return saccades which the model makes from eccentric
starting positions provide a clear example of the way in which
integrating known models into a closed-loop system can highlight
deficiencies in the model.

@@

An examination of the behaviour of the model when presented with
`double-step stimuli' reveals a problem with our inhibitory feedback
connections. We found that when double-step stimuli were presented (where
an initial target at 8\dg~was replaced with a 12\dg~target after 30 or
40~ms) and a double saccade was made [Fig.~\ref{doublesteps}(a), black
lines] the second saccade latency was \e{longer} even than the initial
saccade. This contrasts with \cite{becker_analysis_1979} who find that
second, corrective saccades occur with \e{shorter} latencies.  This
suggests that the inhibitory reset signal implemented in this model is
too strong or has the wrong timescales. This issue highlights the fact
that connections \e{between} component models are quite as important
as the connections within each model.

% Inhibition experimental evidence
\rvw{There is some evidence for an inhibitory projection to SC from the
brainstem. \cite{corvisier_possible_1991} offer evidence for a
projection from the propositus hypoglossi nucleus. This lies upstream
from motoneurons and (in primates) encodes eye
velocity \citep{dale_nucleus_2013}, rather than head movement
velocity. Although the propositus hypoglossi does not lie in exactly
the same functional location as our IBN population (instead it sits
between TN and MN), it offers a possible inhibitory feedback signal
proportional to eye velocity and may help to reduce activity in SC
post-saccade.}
%
\rvwt{Alternatively, it is possible that activity in
FEF and thalamus are reset via a `timed signal'. Feasibly, after
activity in FEF exceeds a threshold, an internal, inhibitory feedback
signal could be activated. This inhibition should have a timescale of
sufficient duration to reduce activity in FEF, thalamus and, via an
increase in inhibitory output from SNr, also in SC. Indeed, the
cortical microcircuit contains a variety of morphologically distinct
gabaergic neurons \citep{douglas_neuronal_2004} which could fulfil
this functionality. A similar mechanism would then be required in SC,
to reset activity generated by direct excitation via the
retinal-collicular pathway which generates express saccades. Again, SC
is a multi-layered structure, containing gabaergic interneurons
\citep{munoz_lateral_1998,meredith_intrinsic_1998,helms_organization_2004,sooksawate_organization_2011}
and there is mounting evidence that saccade dynamics are generated
within
SC \citep{kaneda_regulation_2008,goossens_optimal_2012,bayguinov_hard-wired_2015}. Thus,
a more complex treatment of the SC and FEF regions in the model may
well obviate the need for inhibitory feedback from brainstem to SC,
FEF and thalamus.}

% Reviewer 1's point 2.
\rvw{Considering whether a feedback connection, or internal,
recurrent inhibition is responsible for activity-reset in the brain
model raises a more general question about modelling the central
nervous system. We should consider whether inaccuracies within one
part of the model may propagate errors through the closed-loop system
that cannot be counteracted by another part of the simulation. There
is no way to know, from integrating sub-systems, which properties hold
true, and which are false. However, by integrating models and
examining the behaviour of the combined model, we are presented with
the right questions to ask of the model and the experimental data. In
the case of activity-reset, this is to re-assess whether there exists
inhibitory feedback from brainstem to the SC and FEF regions, and to
find out how an integrated model with self-regulatory mechanisms in SC
and FEF may perform.}

% In a model of SC, \cite{massone_neural-network_1994} suggests that
% internal mechanisms, learned via a supervised method, are sufficient
% to generate dynamics.

@@

@@

% Figure 1
\begin{figure}[t]
\begin{center}
\includegraphics[width=\textwidth]{./figures/ccg_model.png}
\end{center}
\textbf{\refstepcounter{figure}\label{fig:ccg_model} Figure \arabic{figure}.}
{ \bol{a) The macroscopic architecture of the \ccg~model.} The main
nuclei modelled as brain systems are: basal ganglia (BG), frontal eye
fields (FEF), thalamus (THAL) and superior colliculus (SC). The
retinal input is presented via non-biologically plausible retinal
populations. The loops through basal ganglia, which define the
architecture, are shown with coloured lines: the cortical loop
(through FEF and THAL) in green and the sub-cortical loop (through SC
and THAL) in blue. Connections with arrowheads indicate excitatory
connections, those with circles are inhibitory. A red border indicates
that the box represents a sub-system of two or more populations; a
black box indicates (at least, within the context of the model) a
single neural population. The BG box is expanded in: \bol{b) The basal
ganglia model component.}
%
This shows a basal ganglia comprising striatum (Str\_D1 \& Str\_D2),
subthalamic nucleus (STN), globus pallidum externum (GPe) and
substantia nigra reticulata (SNr). The model has three action channels
shown as black boxes within each blue population border. Three
channels of cortical input to the BG are also depicted. Red indicates
the activation level of a given channel, helping to illustrate the
selection mechanism. For example, the channel indicated by the
leftmost bar has a high salience (cortical input) and excites activity
in Str\_D1 which then inhibits the leftmost bar in SNr. The diffuse
projection from STN is equivalent to summing its projections
channel-wise, and then projecting the sum to all channels of its
target populations (the blue arrows indicate that all channels of GPe
and SNr are targeted by the connection). Dopaminergic modulation of
the inputs to the striatum are indicated by the blue circles labelled
`d' and the dotted lines. The SNr sends inhibitory output projections
to its targets. \bol{c) 2D Gaussian weights.} The `GaussianKernel'
connectivity pattern is based on the `in-plane displacement' between
the location of a neural element in one layer, and the location of a
target neural element in the target layer for the connection. The
potential weight of the connection is given by a 2D Gaussian function,
which is maximum for the target neuron which exactly corresponds to
the source neuron, and drops down for target neurons which are
horizontally displaced from the source neuron. A threshold is applied
to avoid a computationally expensive all-to-all connectivity (with
most of these connections having negligible weight values).  If the
weight is non-zero, then a connection is made from source to target,
otherwise no connection is made. \bol{d) Gaussian connectivity.} This
image shows connectivity (green rays) from two source neurons (in
Str\_D2, brown spheres) to target neurons (in GPe, blue spheres). The
circular connectivity pattern is seen. This does not show the weight
\e{values}, which reduce `towards the edge of the circle' and follow the
relationship shown in (c).}
\end{figure}

% Figure 2
\begin{figure}[t]
\begin{center}
\includegraphics[width=0.9\textwidth]{./figures/Brain_Model.png}
\end{center}
\textbf{\refstepcounter{figure}\label{brain_model} Figure \arabic{figure}.}
{ The brain model. This is the SpineCreator `network layer' view of
the model. Each box represents a neural population with 2500 elements,
arranged in a 50$\times$50 grid. The SpineML component name is printed
on the bottom right corner of each population box and the population
name is at the top. The overall connectivity between populations is
represented by the projection arrows with the colour indicating the
connectivity scheme (one-to-one connections are red, Gaussian kernel
connections are dark blue and so on). Excitatory connections have
arrowheads and inhibitory connections have circles, although for
details of the behaviour of the connections, the weight-update and
post-synapse components must be studied. Briefly, the model comprises
a \e{World} population, into which a retinotopically organised view of
the world is introduced. This information is passed into cortical
populations (FEF) and subcortical populations (SC) via a simple model
of the retina. These feed a cortico-thalamo-basal ganglia loop, which
selects which region of the deep layer of superior colliculus should
be disinhibited, allowing activity to build up therein. The five
populations comprising the basal ganglia are enclosed in a grey
outline. Note that substantia nigra pars compacta is not modelled
here, instead the level of dopamine in the striatum is set via a
parameter in the Str\_D1 and Str\_D2 populations}
\end{figure}

% Figure 3
\begin{figure}[t]
\begin{center}
\includegraphics[width=0.9\textwidth]{./figures/mapping.png}
\end{center}
\textbf{\refstepcounter{figure}\label{fig:mapping} Figure \arabic{figure}.}
{ Representative mapping from eye's frame of reference in Cartesian
co-ordinates to retinotopic co-ordinates. (a) The mapping of
luminances in the eye's frame of reference. The world input is
pre-defined by a JSON configuration file. Luminance position, size and
shape can be defined in this file, along with the times at which
luminances appear and disappear. The worldDataMaker.cpp code computes
the locations of the luminances in the eye's frame of reference, given
its rotational state. It also computes a 2D Gaussian convolution of
the luminances. Here, there are two cross shaped luminances spanning
10\dg, one of value 0.8 at the fixation point (0,0) and one of value
0.5 at a peripheral position (0,-12\dg). Note that these crosses have
the same `bar width' of 2\dg~as the crosses used in the simulations,
but their span of 10\dg~is greater than the 6\dg~used in the
simulations, to make these images clearer. (b) The locations of the
luminances in the eye's frame of reference are then converted into
retinotopic co-ordinates, with centrally located luminances being
represented at low values of $r$ and more peripheral luminances having
higher values of $r$. $\phi$ encodes rotational angle: 1 and 50 encode
upward movement; 13 is left; 25 is down; 37 is right. The output of
the World component is fed into FEF\_add\_noise and into the retinal
neuron populations. The colour map makes it possible to distinguish
between the two crosses. (c) The FEF\_add\_noise populations adds a
level of noise to the signal representing processing of the signal in
visual cortex. (d) A Gaussian projection from FEF\_add\_noise to FEF
further blurs the activity in FEF. FEF is the input to the basal
ganglia and one input to superior colliculus.}
\end{figure}

% Figure 4
\begin{figure}[t]
\begin{center}
\includegraphics[width=0.6\textwidth]{./figures/Brain_Stem_1channel.png}
\end{center}
\textbf{\refstepcounter{figure}\label{fig:sbg} Figure \arabic{figure}.}
{ One pair of channels of the saccadic burst generator (SBG) for left
(cyan) or right (green) movements. Collicular activity in SC\_avg
excites the channels via SBG weight maps. Each box represents a neural
population and shows the population name, the number of neural
elements (here 2500 or 1) and the SpineML component name; \e{LIN} for
Leaky integrator or \e{integrator}. Key: LLBN: Long lead burst
neurons; IBN: Inhibitory burst neurons; OPN: Omnipause neurons; EBN:
Excitatory burst neurons; TN: Tonic neurons; MN: Motoneurons.}
\end{figure}

% Figure 5
\begin{figure}[t]
\begin{center}
\includegraphics[width=0.5\textwidth]{./figures/eye_screen_plus.png}
\end{center}
\textbf{\refstepcounter{figure}\label{fig:bioeye} Figure \arabic{figure}.}
{ The biomechanical eye. a) an OpenSim rendering of a pair of
biomechanical eyes showing the positions of the extraocular
muscles. Note that i) volume visualization of muscles should not be
confused with FEM muscle models; it is provided for user feedback
purposes, i.e. shape and color change depending on the muscle
activation, ii) superior and inferior oblique are visualized up to
their respective muscle pulleys. b) OpenSim rendering of biomechanical
eye within a head model c) Top-down schematic cross-sectional view of
the biomechanical eye situated within a spherical screen, with a
horizontal rotation towards a luminances at an angle of $-\theta_{y}$
about the $y$ axis. The $y$ axis points up, out of the page.}
\end{figure}

\begin{figure}[t]
\begin{center}
\includegraphics[width=0.9\textwidth]{./figures/model_framework.png}
\end{center}
\textbf{\refstepcounter{figure}\label{model_framework} Figure \arabic{figure}.}
{ The model framework. The model is specified using a combination of
declarative XML files and hand-coded C++. These original model
specifications are shown within the blue box. b) The green box shows
the processes which are applied to the model specification to produce
the BRAHMS system. Most of the process is defined within the scripts
which make up \stob, but the hand-written components must be manually
compiled and installed within the BRAHMS Namespace, allowing the
BRAHMS executable to locate them at runtime. c) The red box shows the
resulting BRAHMS system ready to be executed by the BRAHMS
executable. In practice, this call is made by \stob.}
\end{figure}

\begin{figure}[t]
\begin{center}
\includegraphics[width=0.9\textwidth]{./figures/scdeep_plus.png}
\end{center}
\textbf{\refstepcounter{figure}\label{scdeep} Figure \arabic{figure}.}
{ a) \& b) Tabareau-style weight maps for `left' and `down' components
of a saccade. c) The two weight maps in a) and b) shown on the same
graph, viewed from above. Circles show the locations of potential
hills of activity. Purple, dashed circles encode saccades down;
red circles encode saccades with both a left and a down component. d)
Showing the additional deep layer of superior colliculus (SC\_deep2)
and the output layer (SC\_avg, named for the fact that in an earlier
version of the model, it received the output of the centroid of
SC\_deep).  The widening Gaussian projection is shown as the arrow
between SC\_deep and SC\_deep2.}
\end{figure}

\begin{figure}[t]
\begin{center}
\includegraphics[width=0.8\textwidth]{./figures/sacc_vs_targetpos.png}
\end{center}
\textbf{\refstepcounter{figure}\label{sacc_vs_targ} Figure \arabic{figure}.}
{ Accuracy at different target eccentricities for fixation luminance
0.2 and target luminance 0.3.}
\end{figure}
